Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness

### 2023-04-03 outputs/paper/paper.qmd
Add files via upload

---
title: "Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness"
subtitle: "An Analysis of the General Social Survey (GSS) Data from 1972 to 2012"
author: 
  - SHAOHAN CHANG
thanks: "Code and data are available at: https://github.com/lucas11333/Factor_of_Wellbeing"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper presents an analysis of a subset of the General Social Survey (GSS) data from the year 1972, which includes information on individuals' demographic characteristics, health, finances, living arrangements, and subjective well-being. The study aimed to explore various aspects of individuals' lives during the early 1970s in the United States, such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.The dataset consists of 5 observations and 10 variables, including year, age, sex, babies, divorce, health, finance_satisfied, living_area, and happy. The study used graphical representation to analyze the relationships between different variables in the dataset and individuals' level of happiness. The results of the analysis suggest that there is a positive relationship between people's satisfaction with their current financial situation, their self-rated health, and their level of happiness in life. Additionally, being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling not too happy. Moreover, the study found that people's level of education is positively associated with their level of happiness in life, as people's education level increases, their level of happiness also gradually increases.Overall, this study provides valuable insights into various aspects of individuals' lives during the early 1970s in the United States. The findings can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being. The study highlights the importance of considering different factors that can influence individuals' level of happiness and well-being, such as their financial situation, health status, and level of education. Further research could investigate more recent data from the GSS to examine changes in these relationships over time."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Surveys are a common method for collecting data on individuals' attitudes, behaviors, and experiences in social science research. One such survey is the General Social Survey (GSS), which has been conducted in the United States since 1972 to 2012. This data set is a subset of the GSS data from the year 1972, which includes information on individuals' demographic characteristics, health, finances, living arrangements, and subjective well-being. While this is a relatively small data set, it provides a glimpse into the lives of individuals in the United States during a particular period in time.This paper aims to explore various aspects of individuals' lives during the early 1970s in the United States using the GSS data set. The variables in this data set are diverse and reflect a range of aspects of individuals' lives. For instance, the variables on babies and divorce provide information on individuals' family structures, while the variables on health and finance satisfaction offer insights into their well-being and financial stability [@b]. The data set also includes variables on individuals' living arrangements and their subjective well-being, providing a glimpse into their social context and overall happiness.

@@

This data-set contains information on various personal and demographic characteristics of individuals, collected between the years 1972 and 2012. The data-set includes variables such as age, sex, number of babies, divorce status, self-reported health status, financial satisfaction, living area, and level of happiness. The data-set can be used to study the relationships between these variables and to gain insights into factors that may influence an individual's overall life satisfaction.

@@

@@

### Baby

@@

### Health

@@

### Financial Satisfaction

@@

### Divorce

@@

### Degree

>>>>

---
title: "Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness"
subtitle: "An Analysis of the General Social Survey (GSS) Data from 1972 to 2012"
author: 
  - SHAOHAN CHANG
thanks: "Code and data are available at: https://github.com/lucas11333/Factor_of_Wellbeing"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper presents an analysis of a subset of the General Social Survey (GSS) data from the year 1972, which includes information on individuals' demographic characteristics, health, finances and subjective well-being. The study aimed to explore various aspects of individuals' lives during the early 1970s in the United States, such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.The dataset consists of 13 observations and 24947 variables, for example: including year, age, sex, babies, divorce, health, finance satisfied and happy. The study used graphical representation to analyze the relationships between different variables in the dataset and individuals' level of happiness. The results of the analysis suggest that there is a positive relationship between people's satisfaction with their current financial situation, their self-rated health, and their level of happiness in life. Additionally, being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling not too happy. Moreover, the study found that people's level of education is positively associated with their level of happiness in life, as people's education level increases, their level of happiness also gradually increases.Overall, this study provides valuable insights into various aspects of individuals' lives during the early 1970s in the United States. The findings can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being. The study highlights the importance of considering different factors that can influence individuals' level of happiness and well-being, such as their financial situation, health status, and level of education. Further research could investigate more recent data from the GSS to examine changes in these relationships over time."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Surveys are a common method for collecting data on individuals' attitudes, behaviors, and experiences in social science research. One such survey is the General Social Survey (GSS), which has been conducted in the United States since 1972 to 2012. This data set is a subset of the GSS data from the year 1972, which includes information on individuals' demographic characteristics, health, finances and subjective well-being. While this is a relatively small data set, it provides a glimpse into the lives of individuals in the United States during a particular period in time.This paper aims to explore various aspects of individuals' lives during the early 1970s in the United States using the GSS data set. The variables in this data set are diverse and reflect a range of aspects of individuals' lives. For instance, the variables on babies and divorce provide information on individuals' family structures, while the variables on health and finance satisfaction offer insights into their well-being and financial stability [@b]. The data set also includes variables on individuals' living arrangements and their subjective well-being, providing a glimpse into their social context and overall happiness.

@@

This data-set contains information on various personal and demographic characteristics of individuals, collected between the years 1972 and 2012. The data-set includes variables such as age, sex, number of babies, divorce status, self-reported health status, financial satisfaction and level of happiness. The data-set can be used to study the relationships between these variables and to gain insights into factors that may influence an individual's overall life satisfaction.

@@

### Analyzing the Impact of Family Size on Happiness

@@

### Exploring the Connection Between Childlessness and Happiness

@@

### The Interplay of Health and Happiness: Evaluating the Link Between Self-Perceived Health and Life Satisfaction

@@

### The Financial Satisfaction-Happiness

@@

### Marital Status and Happiness: Comparing the Emotional Well-Being of Married and Divorced Individuals

@@

### Education and Emotional Well-Being
